Pteropod physiological analysis

### 2018-03-27 figures.Rmd
better labels on correlation heatmap

```{r corplo, fig.height = 6, fig.width = 7}
levs <- c(sort(envchr), sort(biochr), sort(phychr))
prplo <- crs %>% 
  separate(pr, c('cor', 'sig'), sep = ' ') %>% 
  filter(var1 %in% levs & var2 %in% levs) %>% 
  mutate(
    cor = as.numeric(cor), 
    var1 = factor(var1, levels = rev(levs)), 
    var2 = factor(var2, levels = rev(levs)), 
    sig = gsub('ns', '', sig)
  )

pbase <- theme(
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(), 
  axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8), 
  axis.text.y = element_text(size = 8),
  legend.position = 'top', 
  plot.margin = unit(c(0,4,0,0), "lines"),
  strip.background = element_blank(), 
  strip.text.y = element_text(angle = 0, hjust = 0, vjust = 0.5), 
  panel.background = element_rect(fill = 'black')
  )

@@

p <- ggplot(prplo) + 
  geom_tile(aes(y = var1, x = var2, fill = cor), colour = 'black') + 
  geom_text(aes(y = var1, x = var2, label = sig)) +
  annotation_custom(grob = textGrob(label = outlab$lab[1], hjust = 0, gp = gpar(cex = 0.7)),
                    ymin = outlab$y[1], ymax = outlab$y[1], xmin = 23, xmax = 23) +
  annotation_custom(grob = textGrob(label = outlab$lab[2], hjust = 0, gp = gpar(cex = 0.7)),
                    ymin = outlab$y[2], ymax = outlab$y[2], xmin = 23, xmax = 23) +  
  annotation_custom(grob = textGrob(label = outlab$lab[3], hjust = 0, gp = gpar(cex = 0.7)),
                    ymin = outlab$y[3], ymax = outlab$y[3], xmin = 23, xmax = 23) +
  pbase +
  scale_y_discrete('', expand = c(0, 0)) + 
  scale_x_discrete('', expand = c(0, 0)) +
  scale_fill_gradient2('Correlation', low = muted("blue"), mid = "white", high = muted("red"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0))) +
  geom_hline(yintercept = 6.5, size = 1.5) +
  geom_hline(yintercept = 14.5, size = 1.5) +
  geom_vline(xintercept = 6.5, size = 1.5) +
  geom_vline(xintercept = 14.5, size = 1.5)

>>>>

```{r corplo, fig.height = 6, fig.width = 7}
levs <- c(sort(envchr), sort(biochr), sort(phychr))
labs <- c('Omega[ar]', 'CO[3]^-2', 'chla', 'Lat', 'O[2]', 'pCO[2]', 'pH', 'Temp', 'CAT', 'GR', 'GSHonGSSG', 'GST', ' LPX', 'ORAC', 'ORACvLPX', 'SOD', 'abundance', 'dissolution', 'growth', 'scarring', 'typeII', 'typeIII')
prplo <- crs %>% 
  separate(pr, c('cor', 'sig'), sep = ' ') %>% 
  filter(var1 %in% levs & var2 %in% levs) %>%  
  mutate(
    cor = as.numeric(cor), 
    var1 = factor(var1, levels = rev(levs), labels = rev(labs)), 
    var2 = factor(var2, levels = rev(levs), labels = rev(labs)), 
    sig = gsub('ns', '', sig)
  )

pbase <- theme(
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(), 
  axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8), 
  axis.text.y = element_text(size = 8),
  legend.position = c(0.5, 1.12),
  legend.direction = 'horizontal',
  plot.margin = unit(c(4,4,0,0), "lines"),
  strip.background = element_blank(), 
  strip.text.y = element_text(angle = 0, hjust = 0, vjust = 0.5), 
  panel.background = element_rect(fill = 'black')
  )

@@

p <- ggplot(prplo) + 
  geom_tile(aes(y = var1, x = var2, fill = cor), colour = 'black') + 
  geom_text(aes(y = var1, x = var2, label = sig)) +
  annotation_custom(grob = textGrob(label = outlab$lab[1], hjust = 0, gp = gpar(cex = 0.7)),
                    ymin = outlab$y[1], ymax = outlab$y[1], xmin = 23, xmax = 23) +
  annotation_custom(grob = textGrob(label = outlab$lab[2], hjust = 0, gp = gpar(cex = 0.7)),
                    ymin = outlab$y[2], ymax = outlab$y[2], xmin = 23, xmax = 23) +  
  annotation_custom(grob = textGrob(label = outlab$lab[3], hjust = 0, gp = gpar(cex = 0.7)),
                    ymin = outlab$y[3], ymax = outlab$y[3], xmin = 23, xmax = 23) +
  annotation_custom(grob = textGrob(label = outlab$lab[1], hjust = 0.5, gp = gpar(cex = 0.7)),
                    xmin = outlab$y[1], xmax = outlab$y[1], ymin = 23.5, ymax = 23.5) +
  annotation_custom(grob = textGrob(label = outlab$lab[2], hjust = 0.5, gp = gpar(cex = 0.7)),
                    xmin = outlab$y[2], xmax = outlab$y[2], ymin = 23.5, ymax = 23.5) +  
  annotation_custom(grob = textGrob(label = outlab$lab[3], hjust = 0.5, gp = gpar(cex = 0.7)),
                    xmin = outlab$y[3], xmax = outlab$y[3], ymin = 23.5, ymax = 23.5) +
  pbase +
  scale_y_discrete('', expand = c(0, 0), labels = parse(text = rev(labs))) + 
  scale_x_discrete('', expand = c(0, 0), labels = parse(text = rev(labs))) +
  scale_fill_gradient2('Correlation', low = muted("blue"), mid = "white", high = muted("red"), midpoint = 0) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0))) +
  geom_hline(yintercept = 6.5, size = 1.5) +
  geom_hline(yintercept = 14.5, size = 1.5) +
  geom_vline(xintercept = 6.5, size = 1.5) +
  geom_vline(xintercept = 14.5, size = 1.5)
